---
title: "Virginia Tech Beamer Presentation"
author: "Preston Childress"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  beamer_presentation:
    incremental: no
    toc: no
    theme: Hokie
    latex_engine: pdflatex
    slide_level: 2
  ioslides_presentation:
    incremental: no
  slidy_presentation:
    incremental: no
institution: Virginia Tech
subtitle: Some other text
classoption: aspectratio=169
urlcolor: blue
linkcolor: white
header-includes: \AtBeginSection{}
bibliography: citations.bib
biblio-style: apa.csl
nocite: '@rmdGuide, @ggplotBg, @rTheme, @rCodeFont, @rCrime'
---

```{r setup, include=FALSE}
# comment = NA turns off double hash marks on code outputs 
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, comment = NA, dev = 'pdf')
options(width = 120) # Make output wider so more code fits on a widescreen slide.


# This uses a 'size' option in knitr chunks and will change output size. eg {r size="tiny"}
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})


library(ggplot2)
# Transparent background for ggplot helps avoid overlapping the VT logo
theme_update(plot.background = element_rect(fill = "transparent",colour = NA))


# Other libraries can be imported here. 


```


# Intro

## General Stuff

- You can make lists

  - Sub-items are indented
  
    - So are sub-sub-items
    
- And you can do in-line LaTeX: $e^{i\pi} + 1 = 0$

- Or in-line R syntax: `mean(mtcars$mpg)`

- LaTeX blocks are also supported:

$$ \overset{n}{\underset{i=1}{\sum}} \phi_i \frac{\mathbf{u}_i^\intercal \mathbf{b}}{\sigma_i} \mathbf{v}_i $$

# Code Section

## Code Example

- Code outputs with normal font size can use up vertical space quickly

```{r}
# This output is normalsize and takes up space
head(mtcars)
```

## Smaller Code

- The `size` parameter can be used to change code and output size

- It accepts standard LaTeX sizes: 

  - Huge > huge > LARGE > Large > large > normalsize > small > footnotesize > scriptsize > tiny

\footnotesize
```{r, size="footnotesize"}
# This output is footnotesize and takes up less space
head(mtcars)
```

## Plot Example

- Use `fig.width / fig.height` to scale plots

```{r fig.width = 6, fig.height = 2.25, size="footnotesize"}
# Code with {r fig.width = 6, fig.height = 2.25}
qplot(x = mtcars$wt, y = mtcars$mpg)
```

## Handling Overflow {.allowframebreaks}

- Sometimes code output will be too long for a single slide

- Adding `{.allowframebreaks}` to the title of a slide lets it overflow onto a second slide

- For this slide the header is `## Handling Overflow {.allowframebreaks}`

```{r size="footnotesize"}
# Intentionally long output
head(mtcars, 18)
```

- Output is continued to the second slide automatically

- The slide title automatically incremented

- The navigation dot does not advance




# References

## About References

- The References slide is created from a BibTeX `(.bib)` file declared at the top of this file

- Citation style is defined from a `.csl` file also declared at the top of this file

- Use `nocite` to include a citation in the bibliography without referencing it directly

- References can be cited in the presentation with `@referenceName` eg `@ggplotBg`: @ggplotBg

- Zotero is a good tool for building citation files: https://zbib.org/

- There are 1400+ citation style files available: https://github.com/citation-style-language/styles

- `{.allowframebreaks}` can be useful if there are many citations

## References
\footnotesize